Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-10-26 cvx-flats-neurips21/cvx-flats.tex
Addressing comments for camera ready

\author{%
	Jessie Finocchiaro\\%\thanks{Use footnote for providing further information
		%about author (webpage, alternative address)---\emph{not} for acknowledging
	%	funding agencies.} \\
	%Department of Computer Science\\
  University of Colorado Boulder \\
	\texttt{jefi8453@colorado.edu}\raf{better email?}
	% examples of more authors
	\And
	Rafael Frongillo \\
  University of Colorado Boulder \\
	\texttt{raf@colorado.edu}
	\AND
	Bo Waggoner\\
  University of Colorado Boulder \\
	\texttt{bwag@colorado.edu}
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}

@@

\paragraph{Literature on consistency and calibration.}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Defs.~\ref{def:consistent-ell-informal} informally; Defs.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.

When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.and \ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally)\raft{typo def.and?} \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields estimates converging to the correct statistic value.
%\jessiet{Do we still want this following paragraph?}
%\raft{Good question.  I edited a bit, but still up for discussion.}
%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
\begin{table}[h!]
  \vspace*{10pt}
  \begin{center}
    \aboverulesep=1ex
    \belowrulesep=1ex
    \begin{tabular}{p{12ex}ll}
      & \emph{Target loss}  & \emph{Target statistic}\\
      \cmidrule[1pt]{2-3}
%      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1}, e.g. classification  & \textbf{Q2}, e.g. hierarchical classification\\ 
      \cmidrule{2-3}
%      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3}, e.g. least-squares regression & \textbf{Q4}, e.g. variance estimation\\ 
      \cmidrule[1pt]{2-3}
      \\
    \end{tabular}\vspace*{-5pt}
    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.\vspace*{-10pt}}
    \label{tab:quadrants}
  \end{center}
\end{table}
\begin{figure}[h!]
  \centering
  \begin{tikzpicture}[yscale=0.6,xscale=0.46]

@@

    % edges
    \path[->,bend angle=10]
    (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
    (consistent) edge[bend left] node[above, sloped]{Prop.~\ref{thm:consistent-implies-indir-elic}} (indir-elic)    
    (calibrated) edge[bend right] (indir-elic)
    (indir-elic) edge node[above, sloped]{Thm.~\ref{thm:convex-flats-inf-dim}} (d-flats)
    (d-flats) edge[bend right] node[below, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds)
    (d-flats) edge[bend left] node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
  \end{tikzpicture}
\caption{Flow and implications of our results. Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency. In particular, we obtain a testable condition (Theorem~\ref{thm:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate. This condition recovers and strengthens existing calibration-based results for Q1, while simultaneously applying to other quadrants. We illustrate the breadth and power of $d$-flats by resolving two open questions for Q3 and Q4 in \S~\ref{sec:contin-consis}.}
\label{fig:results-flow}
\end{figure}
Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.

As definitions of consistency are difficult to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g. Quadrants 1 and 3. 
Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1.
%, where one is given a target statistic \raf{loss?} and discrete prediction set
We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and derive Proposition~\ref{thm:consistent-implies-indir-elic} via calibration.

@@

\raft{Consistency implies elicitation, so this sentence seems logically incoherent (you can't have the former without the latter.  Recommend reading through this subsection again with fresh eyes.}
Consistency, not necessarily property elicitation, is a prerequisite for deriving error bounds for a loss.
We define consistency here with respect to either a target loss or a property, and show their equivalence in Lemma~\ref{lem:consistent-loss-implies-prop} (\S~\ref{sec:consis-implies-indir}).
In a loose sense, this allows us to ``translate'' the study of consistency for problems in Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4.

@@

Consistency with respect to a property follows similarly, but instead of converging to the optimal target loss, one should approach the optimal property value.

@@

The concept of the link $\psi$ in consistency allows us to think about the application of such a link to a property, which gives rise to the notion of \emph{indirect} elicitation.
In Proposition~\ref{prop:consistent-implies-calibrated}, we connect consistency and elicitation by this observation: if a surrogate is consistent with respect to a property (or loss eliciting that property), then that surrogate and link \emph{indirectly} elicit a that property.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A surrogate loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \reals^d$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}

@@

\begin{restatable}{proposition}{consistencyimpliesindirelic}\label{thm:consistent-implies-indir-elic}
	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{restatable}

@@

\section{Lower bounding convex consistency dimension via $d$-flats}\label{sec:char-convex}
We now turn to the question of bounding the convex consistency dimension for a given task.
From Proposition~\ref{thm:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the convex consistency dimension of $\gamma$.
Theorem~\ref{thm:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
Theorem~\ref{thm:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat} (of codimension $d$).
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
We can then leverage the contrapositive of this result: if $\gamma$ has a level set intricate enough not to contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent convex surrogate.

@@

The following lemma yields consistency bounds when combined with Proposition~\ref{thm:consistent-implies-indir-elic}. %\raft{Minor writing point: we capitalize lemma when it's a proper noun, hence ``this lemma'' vs ``Lemma 1''.  I know, weird.}
% Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} (in Appendix~\ref{app:implications-of-bounds}), which 
A similar result is found in \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Theorem~\ref{thm:convex-flats-inf-dim} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.

@@

\bigskip
\paragraph{Broader impacts via influence on downstream research.}
\jessiet{Taken from original BI statement for this paper}
\raft{Recommend cutting for camera-ready.  Ultimately we just say ``beats me'' at the end, and the rest is not really about broader impacts :-]}
This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
The theory in this paper may help practitioners in a number of ways.
Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.

\begin{ack}
  We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
  This material is based upon work supported by the National Science Foundation under Grant No.\ IIS-2045347.
  \raf{Jessie: GRPF?}
\end{ack}

@@

%Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
Because each target loss in $\L$ elicits some property, but not all target properties can be elicited by a loss (e.g. the variance), consistency with respect to a property is the strictly broader notion.
In a loose sense, Proposition~\ref{lem:consistent-loss-implies-prop} lets us translate problems about target losses to be about the properties these losses elicit.
This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Proposition~\ref{thm:consistent-implies-indir-elic}.

@@

Combining the two results, we can observe the result of Theorem~\ref{thm:consistent-implies-indir-elic} another way: \emph{through calibration}.

>>>>

\author{%
	Jessie Finocchiaro\\%\thanks{Use footnote for providing further information
		%about author (webpage, alternative address)---\emph{not} for acknowledging
	%	funding agencies.} \\
	%Department of Computer Science\\
  University of Colorado Boulder \\
	\texttt{jessica.finocchiaro@colorado.edu}
	% examples of more authors
	\And
	Rafael Frongillo \\
  University of Colorado Boulder \\
	\texttt{raf@colorado.edu}
	\AND
	Bo Waggoner\\
  University of Colorado Boulder \\
	\texttt{bwag@colorado.edu}
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
	% \And
	% Coauthor \\
	% Affiliation \\
	% Address \\
	% \texttt{email} \\
}

@@

\paragraph{Literature on consistency and calibration.}% \label{subsec:consistency}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
%\jessiet{Make this subsection more concise?}
We focus on surrogate losses $L: \reals^d \times \Y \to \reals$ that are consistent, roughly meaning that minimizing $L$-loss corresponds to solving the target problem of interest.
When given a \emph{target loss} $\ell$, we roughly define $L$ to be consistent if minimizing $L$, and applying a link function, minimizes $\ell$ (Def.~\ref{def:consistent-ell-informal} informally; Def.~\ref{def:consistent-ell}, \S~\ref{sec:consis-implies-indir} formally)~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.

When given instead a target statistic such as the conditional quantile or variance, we introduce a notion of consistency in line with classical statistics (Def.~\ref{def:consistent-prop-informal} informally; Def.~\ref{def:consistent-prop}, \S~\ref{sec:consis-implies-indir} formally) \citep{gyorfi2006distribution, fan1998efficient,ruppert1997local}.
Here we define $L$ to be consistent if minimizing $L$ and applying a link function yields predictions converging to the correct statistic value.
%\jessiet{Do we still want this following paragraph?}
%\raft{Good question.  I edited a bit, but still up for discussion.}
%A priori, it is not clear that compatible definitions of consistency could be given for both target statistics and target losses.
The key observation which underpins our approach is that consistency for target losses is a special case of consistency for target statistics (\S~\ref{sec:consis-implies-indir}).
\begin{table}[h!]
  \vspace*{10pt}
  \begin{center}
    \aboverulesep=1ex
    \belowrulesep=1ex
    \begin{tabular}{p{12ex}ll}
      & \emph{Target loss}  & \emph{Target statistic}\\
      \cmidrule[1pt]{2-3}
%      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1:} Classification  & \textbf{Q2:} Hierarchical classification variant\\ 
      \parbox{12ex}{\emph{Discrete \\ prediction}} & \textbf{Q1}, e.g. classification  & \textbf{Q2}, e.g. hierarchical classification\\ 
      \cmidrule{2-3}
%      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3:} Least-squares regression & \textbf{Q4:} Variance estimation\\ 
      \parbox{12ex}{\emph{Continuous \\ estimation}} & \textbf{Q3}, e.g. least-squares regression & \textbf{Q4}, e.g. variance estimation\\ 
      \cmidrule[1pt]{2-3}
      \\
    \end{tabular}\vspace*{-5pt}
    \caption{The four quadrants of problem types, with an example for each as discussed in \S~\ref{sec:illustration}.\vspace*{-10pt}}
    \label{tab:quadrants}
  \end{center}
\end{table}
\begin{figure}[h!]
  \centering
  \begin{tikzpicture}[yscale=0.6,xscale=0.46]

@@

    % edges
    \path[->,bend angle=10]
    (consistent) edge[<->] node[left]{\cite{bartlett2006convexity,steinwart2008support}} (calibrated)
    (consistent) edge[bend left] node[above, sloped]{Prop.~\ref{prop:consistent-implies-indir-elic}} (indir-elic)    
    (calibrated) edge[bend right] (indir-elic)
    (indir-elic) edge node[above, sloped]{Thm.~\ref{thm:convex-flats-inf-dim}} (d-flats)
    (d-flats) edge[bend right] node[below, sloped]{Cor.~\ref{cor:Pcodim-flat-elic-relint-prop}} (q4-bounds)
    (d-flats) edge[bend left] node[above, sloped]{Cor.~\ref{cor:Pcodim-flat-single-val-prop}} (q1-bounds);
  \end{tikzpicture}
\caption{Flow and implications of our results. Compared to calibration, we suggest indirect elicitation as a simpler but almost-as-powerful necessary condition for consistency. In particular, we obtain a testable condition (Theorem~\ref{thm:convex-flats-inf-dim}), based on $d$-flats, for the existence of a $d$-dimensional consistent convex surrogate. This condition recovers and strengthens existing calibration-based results for Q1, while simultaneously applying to other quadrants. We illustrate the breadth and power of $d$-flats by resolving two open questions for Q3 and Q4 in \S~\ref{sec:contin-consis}.}
\label{fig:results-flow}
\end{figure}
Therefore, property elicitation---which studies the exact minimizers of loss functions---allows us to give general lower bounds on prediction dimension of any convex surrogates corresponding to a target task; these bounds apply across all four quadrants.
See \S~\ref{subsec:complexity} for a review of previous work pertaining to notions of prediction dimension.

As definitions of consistency are difficult to apply directly, the literature often focuses on a weaker condition called \emph{calibration}, which only applies when given a target loss, e.g. Quadrants 1 and 3. 
Particularly, several authors~\citep{zhang2004statistical, lin2004note,bartlett2006convexity,tewari2007consistency,ramaswamy2016convex} show the equivalence of consistency and calibration in Quadrant 1.
%, where one is given a target statistic \raf{loss?} and discrete prediction set
We discuss the additional relationship of elicitation and calibration in \S~\ref{app:calibration}, and re-derive Proposition~\ref{prop:consistent-implies-indir-elic} via calibration.

@@

\raft{Consistency implies elicitation, so this sentence seems logically incoherent (you can't have the former without the latter.  Recommend reading through this subsection again with fresh eyes.}
\jessiet{I was trying to build off of: we just talked about elicitation, but who gives a shit about it, since consistency is what we need. Definitely see how it could be confusing to read though.}
%Consistency, not necessarily property elicitation, is a prerequisite for deriving error bounds for a loss.
While property elicitation studies the exact minimizers of a loss, it is not yet clear when and how this can act as a proxy for consistency --- the true condition required for deriving excess risk bounds.
Here, we define consistency here with respect to either a target loss or a property, and show their equivalence in Lemma~\ref{lem:consistent-loss-implies-prop} (\S~\ref{sec:consis-implies-indir}) in our setting.
In a loose sense, this allows us to ``translate'' the study of consistency for problems in Quadrant 1 to Quadrant 2, and from Quadrant 3 to Quadrant 4.

@@

Consistency with respect to a property follows similarly, but instead of converging to the optimal target loss, one should approach the optimal (conditional) property value.

@@

The concept of the link $\psi$ in consistency allows us to think about the application of such a link directly to a property, which gives rise to the notion of \emph{indirect} elicitation.
In Proposition~\ref{prop:consistent-implies-indir-elic}, we connect consistency and elicitation by this observation: if a surrogate is consistent with respect to a property (or loss eliciting that property), then that surrogate and link \emph{indirectly} elicit a that property.
For single-valued properties, this definition reduces to the natural requirement $\gamma = \psi \circ \Gamma$.
\begin{definition}[Indirect Elicitation]\label{def:indirectly-elicits}
	A surrogate loss and link $(L, \psi)$ \emph{indirectly elicit} a property $\gamma:\P \toto \R$ if $L$ elicits a property $\Gamma: \P \toto \reals^d$ such that for all $u \in \reals^d$, we have $\Gamma_u \subseteq \gamma_{\psi(u)}$.
	We say $L$ \emph{indirectly elicits} $\gamma$ if such a link $\psi$ exists.
  \btw{interesting discussion of set-valued properties commented out; revive later!}
\end{definition}

@@

\begin{restatable}{proposition}{consistencyimpliesindirelic}\label{prop:consistent-implies-indir-elic}
	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{restatable}

@@

\section{Lower bounding convex consistency dimension via $d$-flats}\label{sec:char-convex}
We now turn to the question of bounding the convex consistency dimension for a given task.
From Proposition~\ref{prop:consistent-implies-indir-elic}, given a target property $\gamma$ or loss $\ell$ with $\gamma = \prop{\ell}$, this task reduces to lower bounding the convex consistency dimension of $\gamma$.
Theorem~\ref{thm:convex-flats-inf-dim}, crystallized from the proofs of \citet[Theorem 16]{ramaswamy2016convex} and \citet[Theorem 9]{agarwal2015consistent}, considers a particular distribution~$p$ and surrogate prediction $u \in \reals^d$ which is optimal for $p$.
Theorem~\ref{thm:convex-flats-inf-dim} will show that if $d$ is small, then the level set $\{p \in \P : u \in \argmin_{u'} \exploss{L}{u'}{p}\}$ must be large; in fact, it must roughly contain a high-dimensional \emph{flat} (of codimension $d$).
By definition of indirect elicitation, there is some level set $\gamma_r$ (where $u$ is linked to $r$) containing this flat as well.
We can then leverage the contrapositive of this result: if $\gamma$ has a level set intricate enough not to contain any high-dimensional flats, then $\gamma$ cannot have a low-dimensional consistent convex surrogate.

@@

The following lemma yields consistency bounds when combined with Proposition~\ref{prop:consistent-implies-indir-elic}. %\raft{Minor writing point: we capitalize lemma when it's a proper noun, hence ``this lemma'' vs ``Lemma 1''.  I know, weird.}
% Corollaries~\ref{cor:Pcodim-flat-single-val-prop} and~\ref{cor:Pcodim-flat-elic-relint-prop} (in Appendix~\ref{app:implications-of-bounds}), which 
A similar result is found in \citet[Theorem 9]{agarwal2015consistent}, which bounds the dimension of level sets of a single-valued $\prop{L}$.
Theorem~\ref{thm:convex-flats-inf-dim} instead bounds the dimension of flats contained in the level sets, an additional power which we leverage in our examples.

@@

\bigskip
\paragraph{Broader impacts via influence on downstream research.}
\raft{Recommend cutting for camera-ready.  Ultimately we just say ``beats me'' at the end, and the rest is not really about broader impacts :-]}
\jessiet{You're not wrong...}
Since our work is theoretical, it is impossible to forecast downstream applications of this work and their social impact.
%This paper takes a step toward an impactful general program: to understand and design \emph{useful} (i.e. convex, consistent, calibrated, etc.) surrogate losses of low dimensionality.
%The theory in this paper may help practitioners in a number of ways.
%Understanding how to design consistent convex surrogates for different target losses and properties we wish to learn, and when this is impossible, can lead to understanding the tradeoffs that are often made in the current ad-hoc design of surrogates.
%These ad-hoc surrogates are consistent with respect to \emph{some property}, although it may not be the one we wish to predict, either directly or indirectly.
%As a general prediction task arises, one might be able to use property elicitation to understand what question they are actually answering (in the best case, with sufficient data that matches the real-world data distribution) by minimizing their surrogate loss and how it differs from the question they are actually trying to answer.
%Of course, improvements in general machine learning algorithms can be put to many uses in many societal contexts, so a more specific analysis of potential broader impacts is very difficult to forecast.

\begin{ack}
  We thank Adam Bloniarz and Nishant Mehta for several key suggestions and insights.
  This material is based upon work supported by the National Science Foundation under Grant Nos.\ IIS-2045347 and 2040434. \jessie{confirm GRFP number}
\end{ack}

@@

%Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
Because each target loss in $\L$ elicits some property, but not all target properties can be elicited by a loss (e.g. the variance), consistency with respect to a property is the strictly broader notion.
In a loose sense, Proposition~\ref{lem:consistent-loss-implies-prop} lets us translate problems about target losses to be about the properties these losses elicit.
This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Proposition~\ref{prop:consistent-implies-indir-elic}.

@@

Combining the two results, we can observe the result of Proposition~\ref{prop:consistent-implies-indir-elic} another way: \emph{through calibration}.
